### 2022-06-12 paper.tex
changed date
fixed capitalization in bibliography

March 2022
\vspace{6ex}
}]
\blfootnote{\hspace{-.5cm}\raggedright\textsuperscript{*} e-mail:  \texttt{l.kremer@dkfz-heidelberg.de} and\\ \hspace{1cm}\texttt{simon.anders@bioquant.uni-heidelberg.de}}
\section{Abstract}

@@

\subsection{Re-analysis of published scBS datasets}
To re-analyze scBS data sets by \citet{luo2017single} and \citet{argelaguet2019gastru}, the genome was first annotated with genomic intervals that were either obtained by tiling the genome into non-overlapping 100~kb bins, or by acquiring VMRs with \texttt{scbs scan} using default options. For all intervals (VMRs and tiles), the mean methylation fractions and mean shrunken residuals were obtained with \texttt{scbs matrix}. Intervals containing less than four measured CpGs, or that were measured in less than 10\% of cells, were discarded. To select $n$ intervals for further analysis, the top $n$ intervals were picked based on the number of cells that the region was measured in. 
For dimensionality reduction, missing values were imputed with an iterative PCA as described above. To visualize data, UMAP was performed on the final 15 principal components.

@@

The nearest neighbor count score $nnc(k)$ is based on the $\Gamma$-score \citep{Kireeva_2014}. Each cell $c_j^i$ belongs to a cell type $j$. For each cell, $k$ nearest neighbors $nn_j^k$ were computed based on their Euclidean distance. Based on the cell type $j$ of the $k$ nearest neighbors of each cell, the nnc score $nnc(k)$ was computed with formula (1), in which $d(c_j^i, k_j^i)=1$ if at least 90\% of neighbor classes match the class of cell $c_j^i$ and $d(c_j^i, k_j^i)=0$ if less than 90\% of classes match, while $n$ are the total number of cells.
\begin{equation}
    nnc(k) = \frac{1}{n}d(c_j^i, k_j^i)
\end{equation}

>>>>

June 2022
\vspace{6ex}
}]
\blfootnote{\hspace{-.5cm}\raggedright\textsuperscript{*} e-mail:  \texttt{l.kremer@dkfz-heidelberg.de} and\\ \hspace{1cm}\texttt{simon.anders@bioquant.uni-heidelberg.de}}
\section{Abstract}

@@

\subsection{Re-analysis of published scBS datasets}
To re-analyze scBS data sets by \citet{luo2017single} and \citet{argelaguet2019gastru}, the genome was first annotated with genomic intervals that were either obtained by tiling the genome into non-overlapping 100~kb bins, or by acquiring VMRs with \texttt{scbs scan} using default options. \todo{Mention choice of top 1000 regions.} For all intervals (VMRs and tiles), the mean methylation fractions and mean shrunken residuals were obtained with \texttt{scbs matrix}. Intervals containing less than four measured CpGs, or that were measured in less than 10\% of cells, were discarded. To select $n$ intervals for further analysis, the top $n$ intervals were picked based on the number of cells that the region was measured in. 
For dimensionality reduction, missing values were imputed with an iterative PCA as described above. To visualize data, UMAP was performed on the final 15 principal components.

@@

\todo{Improve wording} The nearest neighbor count score $nnc(k)$ is based on the $\Gamma$-score \citep{Kireeva_2014}. Each cell $c_j^i$ belongs to a cell type $j$. For each cell, $k$ nearest neighbors $nn_j^k$ were computed based on their Euclidean distance. Based on the cell type $j$ of the $k$ nearest neighbors of each cell, the nnc score $nnc(k)$ was computed with formula (\todo{ref}), in which $d(c_j^i, k_j^i)=1$ if at least 90\% of neighbor classes match the class of cell $c_j^i$ and $d(c_j^i, k_j^i)=0$ if less than 90\% of classes match, while $n$ are the total number of cells.
\begin{equation}
    \text{nnc}(k) = \frac{1}{n}d(c_j^i, k_j^i)
\end{equation}
